BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-13 Msc-Slides/main.tex
Slides outline complete

@@

\begin{frame}
    \frametitle{API Hooking}

	    \begin{beamerboxesrounded}[shadow=true]{API Hooking}
    Generate random values for {\tt a} and {\tt b}: execute on these inputs and track path constraints. Negate constraints on the branch in order to generate new inputs that will explore the error path.
    \end{beamerboxesrounded}

@@

>>>>

\lstset{escapeinside={<@}{@>}}

@@

\begin{frame}
    \frametitle{Implementation of function call monitoring}

	    \begin{beamerboxesrounded}[shadow=true]{API Hooking}
    The interception of function calls provided by dynamically
linked \\ libraries (DLLs)
    \end{beamerboxesrounded}
    \bigskip
	Three broad categories:

    \begin{itemize}
    \item Binary Rewriting
    \begin{itemize}
    \item Call Redirection
    \item Function Rewriting
    \end{itemize}
    \item Virtual Machine Introspection (VMI)
    \item \textbf{Dynamic Binary Instrumentation (DBI)}
    \end{itemize}

\begin{frame}[fragile]
    \frametitle{Dynamic Binary Instrumentation (DBI)}

A dynamic binary analysis
technique in which the behaviour of an application is inspected at run-time via the
injection of analysis code. 
\bigskip
\begin{block}{}
\begin{lstlisting}[basicstyle=\ttfamily\large,xleftmargin=50pt]
<@\textcolor{red}{record(arg1)}@> 
retval = libcall(arg1, &arg2)
<@\textcolor{red}{record(retval, *arg2)}@> 
\end{lstlisting}
\end{block}
\bigskip
\textbf{Problem 1}: existing products have limited logging capabilites

@@

\begin{frame}
    \frametitle{The threat posed by evasive malware}

		    \begin{beamerboxesrounded}[shadow=true]{API Hooking}
    The interception of function calls provided by dynamically
linked \\ libraries (DLLs)
    \end{beamerboxesrounded}
    \bigskip

\section{BlueTracer}

\begin{frame}
    \frametitle{Our solution: BlueTracer}

\subsection{Intel Pin}

\begin{frame}
    \frametitle{Intel Pin}

\subsection{BluePill}

\begin{frame}
    \frametitle{Integration with BluePill}

\subsection{Architecture}

\begin{frame}
    \frametitle{BlueTracer's architecture}

\section{Evaluation}

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Al-Khaser}

\begin{frame}
    \frametitle{Sample tracked evasive check}

\subsection{Evasive malware samples}
\begin{frame}
    \frametitle{Evasive malware samples}

\section{Conclusions}

\begin{frame}
    \frametitle{Conclusion and future developments}

\begin{frame}
	Thanks for the attention.
\end{frame}
